An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-02-14 Paper.tex
Remove extra patter from the supporting results appendix

\newcommand{\aic}{\textsc{aic}}
\newcommand{\bic}{\textsc{bic}}
\newcommand{\brc}{\textsc{brc}}
\newcommand{\cdf}{\textsc{cdf}}
\newcommand{\clt}{\textsc{clt}}
\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
\newcommand{\dgp}{\textsc{dgp}}
\newcommand{\fclt}{\textsc{fclt}}
\newcommand{\fwe}{\textsc{fwe}}
\newcommand{\gdp}{\textsc{gdp}}
\newcommand{\hac}{\textsc{hac}}
\newcommand{\lln}{\textsc{lln}}
\newcommand{\ma}{\textsc{ma}}
\newcommand{\mds}{\textsc{mds}}
\newcommand{\ned}{\textsc{ned}}
\newcommand{\ols}{\textsc{ols}}
\newcommand{\oos}{\textsc{oos}}
\newcommand{\sfwe}{\textsc{sfwe}}
\newcommand{\spa}{\textsc{spa}}
\newcommand{\wfwe}{\textsc{wfwe}}

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size
    $-\frac12$ on the series $V_t$; $V_t$ is strong mixing of size
    $-\frac{r}{r-2}$ or uniform mixing of size $-\frac{r}{2r-2}$ with
    $r > 2$.\footnote{For uniform mixing processes, $r = 2$ is also
      allowed as long as $\sup_{\beta \in N} \psi_t(\beta)^2$ and
      $\sup_{\beta \in N} (\partial \psi_t(\beta) / \partial \beta)^2$
      are uniformly integrable; these terms are defined later in these
      assumptions.}  Moreover, the \ned-coefficients are uniformly
    bounded.
  \item The sequence $(y_1^{*}, z_t^*),\dots,(y_T^{*}, z_T^*)$ is
    generated by the moving blocks, circular blocks, or stationary
    bootstrap with block lengths drawn from the geometric
    distribution.  The (expected) block length $b$ satisfies $b \to
    \infty$ and $\frac{b}{P} \to 0$.
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s} & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s} & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s} & \text{fixed window} \\
      \end{cases}
    \end{equation}
    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
    $\E h_{s} = 0$ for all $s$; and $\frac12 \sum_{t=1}^T h_t^* = 0$
    a.s. where $h_t^* = h(y_s^*, z_s^*, \hat\beta_T)$.  Also define
    \begin{equation}
      H_{t}^* = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}^* & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}^* & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}^* & \text{fixed window} \\
      \end{cases}
    \end{equation}
  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
    the asymptotic variance matrix of $\bar{f}(\beta_0)$ is uniformly
    positive definite.
  \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
    $\psi_t(\beta)$ is covariance stationary and is continuously
    differentiable in an open neighborhood $N$ of $\beta_0$.  Also,
    $\E( \sup_{\beta \in N} |\psi_t(\beta)|)^r$ and $\E\sup_{\beta \in
      N} |\frac{\partial \psi_t(\beta)}{\partial \beta}|^2$ are
    uniformly bounded.
  \item $R, P \to \infty$ as $T \to \infty$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

\begin{rem}
  \citet{Mcc:00} proves asymptotic normality under weaker smoothness
  condtions on $f_t(\beta)$ and $h_t(\beta)$: only their expectations
  must be continuously differentiable.  It may be possible to extend
  Theorem~\ref{res:3} to those weaker conditions, but the current
  proof relies on a theorem of \citepos{JoD:00} establishing the
  consistency of \hac\ estimators which requires differentiability of
  the observations.  Extending \citepos{JoD:00} result to
  nondifferentiable functions should be possible, but is beyond the
  scope of this paper.
\end{rem}

@@

\begin{rem}
  \citet{CoS:07} use the distribution of $\sqrt{P}(\bar{f}^{*} -
  \bar{f})$ to approximate that of $\sqrt{P}(\bar{f} - \E
  \bar{f}(\beta_0))$.  But it is clear that $\bar{f}(\hat{\beta}_T)$
  is the bootstrap analogue of $\E \bar{f}(\beta_0)$, the parameter of
  interest.  Because their bootstrap is miscentered, \citet{CoS:07}
  must redefine $\hat{\beta}_t^{*}$ to achieve consistency.  In this
  paper, though, consistency arises naturally.
\end{rem}

@@

\begin{proof}[Proof of Theorem \ref{res:2}]
  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
  Theorem~\ref{res:3} of this paper, Theorem~3.1 and~4.1 of
  \citet{RoW:05}, and Theorem~1 of \citet{Cal:11e} complete the proof.
\end{proof}

@@

\section{Supporting Results}
This Appendix restates \citepos{Mcc:00} results, which themselves
weaken \citepos{Wes:96} assumptions, but under the dependence
conditions of Theorem~\ref{res:1}.  It also proves Lemmas required for
that result and the results in the main paper.

@@

\begin{lema}\label{res:a3}
  Suppose the conditions of Theorem~\ref{res:3} hold and let
  \[\psi_t^{*}(\beta) = 
  \binom{f_t^{*}(\beta) - \bar{f}(\beta)}{h_t^{*}(\beta) - \bar h(\beta)}.\]
  Then
  \begin{equation}\label{eq:1}
    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}^{*}(\hat\beta_T)
    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}(\beta_0)
    \leq x \Big] \Big| > \epsilon \Big] \to 0
  \end{equation}
  for all positive $\epsilon$.
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a3}]
  Note that $\psi_t$ satisfies a \clt, \citep[Theorem~2]{Jon:97}; the
  bootstrap average obeys a \clt\ as well from
  \citet[Theorem~2]{Cal:11d}, so it suffices to prove that
  \[ \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^*( \hat
  \beta_T ) \Big) - \tfrac{ 1 }{ P } \var \Big( \sum_{t=R+1}^T \psi_t(
  \beta_0 ) \Big) \to^p 0. \] I will prove this result for the Moving
  Blocks Bootstrap---the proof for other block bootstraps is similar
  and follows as in \cite{Cal:11d}.

@@

  Note that
  \begin{equation*}
  \tfrac{ 1 }{ P } \var^* \Big( \sum_{ t = R + 1 }^T \psi_t^*( \hat \beta_T ) \Big)
  = \su \hat \psi_s( \hat \beta_T ) \hat \psi_t( \hat \beta_T )'
     - \tilde \psi( \hat \beta_T ) \tilde \psi( \hat \beta_T )'
  \end{equation*}
  where
  \begin{equation*}
    \tilde \psi( \hat \beta_T )
    = \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
       + \tfrac{ 1 }{ T - b } \sum_{ t = 1 }^b \tfrac{ t }{ b }
         \big( \psi_t( \hat \beta_T ) + \psi_{ T - t + 1 }( \hat \beta_T ) \big)
  \end{equation*}
  Since $\bar \psi( \hat \beta_T ) = 0$ by construction and (finish explanation), we have
  \begin{align*}
    \tilde \psi( \hat \beta_T )
    &= \tfrac{ b }{ T } \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
       + \tfrac{ 1 }{ T - b } \sum_{ t = 1 }^b 
       \Big( \tfrac{ t - b }{ b } - \tfrac{ b }{ T } \Big)
       \big( \psi_t( \hat \beta_T ) + \psi_{ T - t + 1 }( \hat \beta_T ) \big) \\
    &= o_p(1).
  \end{align*}
  Moreover,
  \begin{equation*}
    \su \hat\psi_s \hat\psi_t' \to^p \var \Big( \sum_{t=R+1}^T \psi_t \Big)
  \end{equation*}
  by \citet[Theorem 2.2]{JoD:00}.  To see this, observe that 
  \begin{equation*}
    \su \hat\psi_s \hat\psi_t' 
    = \tfrac{1}{T} \sum_{s,t=1}^T \hat\psi_s \hat\psi_t' \;
      \big(1 - \tfrac{\lvert s - t \rvert}{b}\big)^+ + term.
  \end{equation*}
  The first term satisfies most of \citepos{JoD:00} Assumptions by
  construction and it suffices to prove their condition (2.9) holds,
  namely that
  \begin{equation}\label{eq:2}
    \sup_{\beta \in N} \Bigg\lVert \tfrac{1}{T} \sum_{t=1}^T e^{i \xi t/b} 
    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg) 
    \Bigg\rVert_2 \to 0
  \end{equation}
  for all $i$, $j$, and $\xi$.  I will show that \eqref{eq:2} holds
  for the real part of the expression; the proof for the complex part
  is similar.

  For any fixed $\beta \in N$,
  \begin{equation*}
    \tfrac{1}{T} \sum_{t=1}^T \cos( \xi t / b )
    \Bigg( \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} - 
          \E \frac{\partial \psi_{jt}(\beta)}{\partial \beta_i} \Bigg) 
  \end{equation*}
  obeys an \lln\ (give reference and explanation -- you need to show
  that the derivatives are \ned\ as well.) and convergence in $L_2$
  follows from uniform integrability.

  TODO: add stochastic equicontinuity conditions.
\end{proof}

>>>>

\newcommand{\aic}{\textsc{aic}}
\newcommand{\bic}{\textsc{bic}}
\newcommand{\brc}{\textsc{brc}}
\newcommand{\cdf}{\textsc{cdf}}
\newcommand{\clt}{\textsc{clt}}
\newcommand{\dd}[1]{\frac{\partial}{\partial #1}}
\newcommand{\dgp}{\textsc{dgp}}
\newcommand{\fclt}{\textsc{fclt}}
\newcommand{\fwe}{\textsc{fwe}}
\newcommand{\gdp}{\textsc{gdp}}
\newcommand{\hac}{\textsc{hac}}
\newcommand{\ma}{\textsc{ma}}
\newcommand{\mds}{\textsc{mds}}
\newcommand{\ned}{\textsc{ned}}
\newcommand{\ols}{\textsc{ols}}
\newcommand{\oos}{\textsc{oos}}
\newcommand{\sfwe}{\textsc{sfwe}}
\newcommand{\spa}{\textsc{spa}}
\newcommand{\wfwe}{\textsc{wfwe}}

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item Let $\{y_t, z_t\}$ be an $L_2$-\ned\ process of size $-\frac12$ on
    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
    > 2$.
  \item The sequence $(y_1^{*}, z_t^*),\dots,(y_T^{*}, z_T^*)$ is
    generated by the moving blocks, circular blocks, or stationary
    bootstrap with block lengths drawn from the geometric
    distribution, and $b$ satisfies $b \to \infty$ and $\frac{b}{P}
    \to 0$; $b$ is the block length of the moving or circular blocks
    bootstraps and is the expected block length of the stationary
    bootstrap.
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s} & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s} & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s} & \text{fixed window} \\
      \end{cases}
    \end{equation}
    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
    $\E h_{s} = 0$ for all $s$; and $\frac12 \sum_{t=1}^T h_t^* = 0$
    a.s. where $h_t^* = h(y_s^*, z_s^*, \hat\beta_T)$.  Also define
    \begin{equation}
      H_{t}^* = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}^* & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}^* & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}^* & \text{fixed window} \\
      \end{cases}
    \end{equation}
  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
    $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
  \item Each element of $\E f_{t}(\beta)$ is continuously
    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
  \item $R, P \to \infty$ as $T \to \infty$.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite and $\E f_t(\beta_0) = \E
    f_s(\beta_0)$ for all $s$ and $t$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\begin{rem}
  \citet{CoS:07} use the distribution of $\sqrt{P}(\bar{f}^{*} -
  \bar{f})$ to approximate that of $\sqrt{P}(\bar{f} - \E
  \bar{f}(\beta_0))$.  But it is clear that
  $\bar{f}(\hat{\beta}_{T+1})$ is the bootstrap analogue of $\E
  \bar{f}(\beta_0)$, the parameter of interest.  Because their
  bootstrap is miscentered, \citet{CoS:07} must redefine
  $\hat{\beta}_t^{*}$ to achieve consistency.  In this paper, though,
  consistency arises naturally.
\end{rem}

@@

\begin{proof}[Proof of Theorem \ref{res:2}]
  Replace $R$ and $P$ as in the proof of Theorem~\ref{res:1}.
  Theorem~\ref{res:3} of this paper and Theorems~3.1 and~4.1 of
  \citet{RoW:05} complete the proof.
\end{proof}

@@

\section{Supporting Results}

@@

\begin{lema}\label{res:a3}
  Suppose the conditions of Theorem~\ref{res:3} hold; let $\psi_{t} =
  (f_{t}' - \E f_{t}', a_t h_{t}')'$ and $\psi_t^{*} =
  (f_t^{*}(\hat{\beta}_{T+1})' - \bar{f}(\hat{\beta}_{T+1})',
  h_t^{*\prime})'$.  Then
  \begin{equation}\label{eq:1}
    \pr\Big[\sup_x \Big| \pr^{*}\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}^{*}
    \leq x \Big] - \pr\Big[ \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \psi_{t}
    \leq x \Big] \Big| > \epsilon \Big] \to 0
  \end{equation}
  for all positive $\epsilon$.
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a3}]
  Note that $\psi_t$ satisfies a \clt, \citep[Theorem~2]{Jon:97}; the
  bootstrap average obeys a \clt\ as well from
  \citet[Theorem~2]{Cal:11d} and is asymptotically normal, so it
  suffices to prove that
  \[ \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^* \Big) -
  \tfrac{ 1 }{ P } \var \Big( \sum_{t=R+1}^T \psi_t \Big) \to^p 0. \]
  I will prove this result for the Moving Blocks Bootstrap---the proof
  for other block bootstraps is similar and follows as in
  \cite{Cal:11d}.

@@

  Note that
  \begin{equation*}
  \tfrac{ 1 }{ P } \var^* \Big( \sum_{t=R+1}^T \psi_t^* \Big)
  = \su \hat\psi_s \hat\psi_t'
     - \tilde \psi( \hat \beta_T ) \tilde \psi( \hat \beta_T )'
  \end{equation*}
  where
  \begin{equation*}
    \tilde \psi( \hat \beta_T
    = \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
       + \tfrac{ 1 }{ T - b } \sum_{ t = 1 }^b \tfrac{ t }{ b }
         \big( \psi_t( \hat \beta_T ) + \psi_{ T - t + 1 }( \hat \beta_T ) \big)
  \end{equation*}
  Since $\bar \psi( \hat \beta_T ) = 0$ by construction and (finish explanation), we have
  \begin{align*}
    \tilde \psi( \hat \beta_T )
    &= \tfrac{ b }{ T } \tfrac{ 1 }{ T - b } \sum_{ t = b + 1 }^{ T - b } \psi_t( \hat \beta_T )
       + \tfrac{ 1 }{ T - b } \sum_{ t = 1 }^b 
       \Big( \tfrac{ t - b }{ b } - \tfrac{ b }{ T } \Big)
       \big( \psi_t( \hat \beta_T ) + \psi_{ T - t + 1 }( \hat \beta_T ) \big) \\
    &= o_p(1).
  \end{align*}
  Moreover,
  \begin{equation*}
    \su \hat\psi_s \hat\psi_t' \to^p \var \Big( \sum_{t=R+1}^T \psi_t \Big)
  \end{equation*}
  by (de Jong and Davidson reference), completing the proof.
\end{proof}
